Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-01-20 paper_comparison/paper_comparison/paper_comparison.Rmd
working onrejection rate stats

```{r p-value-comparison, fig.width=8, fig.height=4, fig.cap="Rejection rate of visual test conditional on the conventional test decision on non-linearity (left) and heteroskedasticity (right) lineups (uniform fitted values only) displayed using a mosaic plot. The visual test rejects less frequently than the conventional test. We would generally expect that the visual test would only reject when the conventional test does. Surprisingly, this is not what we see: the visual test sometimes rejects when the conventional test doesn't. "}

@@

(remove lineup id from caption)

@@

For lineups produced by the non-linearity model, 25% are rejected by both the conventional and visual tests, while 42% are accepted by both tests. Thus, 69% of the time two tests will agree with each other. There are 26% of lineups rejected by conventional tests only.

>>>>

```{r p-value-comparison, fig.width=8, fig.height=4, fig.cap="Rejection rate ($p$-value $<0.05$) of visual test conditional on the conventional test decision on non-linearity (left) and heteroskedasticity (right) lineups (uniform fitted values only) displayed using a mosaic plot. The visual test rejects less frequently than the conventional test. We would generally expect that the visual test would only reject when the conventional test does. Surprisingly, this is not what we see: the visual test sometimes rejects when the conventional test doesn't. "}

@@

@@

For lineups produced by the non-linearity model, conventional tests reject `r p_value_cmp_dat %>% filter(type == "non-linearity") %>% count(conv_reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% 
and visual tests reject `r p_value_cmp_dat %>% filter(type == "non-linearity") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% of the time. Of the tests rejected by the conventional test, `r p_value_cmp_dat %>% filter(type == "non-linearity") %>% filter(conv_reject == "Reject") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`%, so approximately half as many as the conventional test. Surprisingly, the visual test rejects `r p_value_cmp_dat %>% filter(type == "non-linearity") %>% filter(conv_reject == "Not") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% of lineups where the conventional test does not reject.

are rejected by both the conventional and visual tests, while 42% are accepted by both tests. Thus, 69% of the time two tests will agree with each other. There are 26% of lineups rejected by conventional tests only.

### 2023-01-20 paper_comparison/paper_comparison/paper_comparison.tex
working onrejection rate stats

\caption{Rejection rate of visual test conditional on the conventional test decision on non-linearity (left) and heteroskedasticity (right) lineups (uniform fitted values only) displayed using a mosaic plot. The visual test rejects less frequently than the conventional test. We would generally expect that the visual test would only reject when the conventional test does. Surprisingly, this is not what we see: the visual test sometimes rejects when the conventional test doesn't. }\label{fig:p-value-comparison}
\end{figure}

(remove lineup id from caption)

@@

For lineups produced by the non-linearity model, 25\% are rejected by
both the conventional and visual tests, while 42\% are accepted by both
tests. Thus, 69\% of the time two tests will agree with each other.
There are 26\% of lineups rejected by conventional tests only.

>>>>

\caption{Rejection rate ($p$-value $<0.05$) of visual test conditional on the conventional test decision on non-linearity (left) and heteroskedasticity (right) lineups (uniform fitted values only) displayed using a mosaic plot. The visual test rejects less frequently than the conventional test. We would generally expect that the visual test would only reject when the conventional test does. Surprisingly, this is not what we see: the visual test sometimes rejects when the conventional test doesn't. }\label{fig:p-value-comparison}
\end{figure}

@@

For lineups produced by the non-linearity model, conventional tests
reject 51\% and visual tests reject 32\% of the time. Of the tests
rejected by the conventional test, 49\%, so approximately half as many
as the conventional test. Surprisingly, the visual test rejects 14\% of
lineups where the conventional test does not reject.

are rejected by both the conventional and visual tests, while 42\% are
accepted by both tests. Thus, 69\% of the time two tests will agree with
each other. There are 26\% of lineups rejected by conventional tests
only.
